---
title: "Chapter Annual Reports for 2019 - Data and Text Summary"
author: "Melinda Higgins, PhD; Vice-Chair District 5"
date: "8/1/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# set up knitr options
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

# read in data
library(readxl)
data2019 <-
  read_excel("ChapterAnnualReport-2019.xlsx")

```

## 2019 Annual Chapter Reports from 2019

The Excel file containing all of the 2019 Annual ASA Chapter Reports was downloaded from the ASA Leader Hub - under Annual Chapter Reports. Go to [https://ww2.amstat.org/MembersOnly/chapterreportsnew/adminreportstatus_districts.cfm](https://ww2.amstat.org/MembersOnly/chapterreportsnew/adminreportstatus_districts.cfm) logged in with an ASA leader/officer account.

Summaries are provide for each part of the questionnaire by district and region.

## Breakdown of Reports submitted by Region and District

```{r}
library(dplyr)
library(ggplot2)
library(janitor)

data2019 %>%
  tabyl(DISTRICT, REGION)

data2019 %>% 
  filter((DISTRICT == 4) & (REGION == 3)) %>%
  select(1:4)

data2019 %>%
  ggplot(aes(DISTRICT)) +
  geom_bar(aes(fill = as.factor(REGION)))
  coord_flip()
```

## Other Chapter Activities

look at single words as tokens

```{r}
# look at other activities text entries
# extract reportid and chaptername with text cokumn
other_words <- data2019 %>%
  select(REPORTID, CHAPTERNAME, TXTOTHERACTIVITIES)

library(tidytext)
other_words_tidy <- other_words %>%
  unnest_tokens(word, TXTOTHERACTIVITIES)

# load stop_words
data(stop_words)

# add custom stop words for ASA chapters
addwords <- data.frame(c("2019","chapter","statistics","asa"), 
                       c("mkh","mkh","mkh","mkh"))
names(addwords) <- names(stop_words)
stop_words2 <- rbind(stop_words, addwords)

# filter our NAs and
# remove stop_words using anti_join()
other_words_tidy_rmstop <- other_words_tidy %>%
  filter(complete.cases(.)) %>%
  anti_join(stop_words2)

# get table summary of most used words
other_words_tidy_rmstop %>%
  count(word, sort = TRUE)

# use ggplot sorted bar graph
other_words_tidy_rmstop %>%
  count(word, sort = TRUE) %>%
  filter(n > 2) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  ggtitle("Other Chapter Activities - Single Words")
  
# word cloud - not very interesting...
library(wordcloud)
other_words_tidy_rmstop %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))


chptr_other_words_tidy <- data2019 %>%
  select(REPORTID, DISTRICT, CHAPTERNAME, TXTOTHERACTIVITIES) %>%
  unnest_tokens(word, TXTOTHERACTIVITIES) %>%
  filter(complete.cases(.)) %>%
  anti_join(stop_words2) %>%
  count(DISTRICT, word, sort=TRUE) %>%
  ungroup()

chptr_other_words_total <- chptr_other_words_tidy %>%
  group_by(DISTRICT) %>%
  summarise(total = sum(n))

chptr_other_words <- left_join(chptr_other_words_tidy,
                               chptr_other_words_total)

ggplot(chptr_other_words, aes(n/total, fill = DISTRICT)) +
  geom_histogram(show.legend = FALSE) +
  facet_wrap(~DISTRICT, ncol=2, scales = "free_y")

chptr_other_words <- chptr_other_words %>%
  bind_tf_idf(word, DISTRICT, n)

chptr_other_words

chptr_other_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(DISTRICT) %>% 
  top_n(2) %>% 
  ungroup() %>%
  ggplot(aes(word, tf_idf, fill = DISTRICT)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~DISTRICT, ncol = 2, scales = "free") +
  coord_flip() +
  ggtitle("Highest tf-idf words by District")


```

try tokens = "ngrams" for n=2

```{r}
otheract_bigrams <- data2019 %>%
  select(REPORTID, DISTRICT, CHAPTERNAME, TXTOTHERACTIVITIES) %>%
  unnest_tokens(bigram, TXTOTHERACTIVITIES,
                token = "ngrams", n = 2)

library(tidyr)
otheract_bigrams_separated <- otheract_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

otheract_bigrams_filtered <- otheract_bigrams_separated %>%
  filter(!word1 %in% stop_words2$word) %>%
  filter(!word2 %in% stop_words2$word) %>%
  filter(complete.cases(.))

# new bigram counts:
otheract_bigrams_counts <- otheract_bigrams_filtered %>% 
  count(word1, word2, sort = TRUE)

otheract_bigrams_counts

otheract_bigrams_united <- otheract_bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")

otheract_bigrams_united

library(igraph)

# filter for only relatively common combinations
bigram_graph <- otheract_bigrams_counts %>%
  filter(n > 1) %>%
  graph_from_data_frame()

bigram_graph

library(ggraph)
set.seed(2017)

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  ggtitle("Common bigrams in Other Activities")
```

