---
title: "Chapter Annual Reports for 2019 - Summaries of Text Responses"
author: "Melinda Higgins, PhD; Vice-Chair District 5"
date: "8/3/2020"
output:
  powerpoint_presentation: default
  beamer_presentation: default
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
# set up knitr options
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(error = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

# read in data
library(readxl)
data2019 <-
  read_excel("ChapterAnnualReport-2019.xlsx")
```

## 2019 Annual Chapter Reports from 2019

The Excel file containing all of the 2019 Annual ASA Chapter Reports was downloaded from the ASA Leader Hub - under Annual Chapter Reports. Go to [https://ww2.amstat.org/MembersOnly/chapterreportsnew/adminreportstatus_districts.cfm](https://ww2.amstat.org/MembersOnly/chapterreportsnew/adminreportstatus_districts.cfm) logged in with an ASA leader/officer account.

```{r dataftns}
# set up libraries
library(dplyr)
library(ggplot2)
library(janitor)
library(tidytext)
library(wordcloud)
library(tidyr)

# set up processing of text fields
# load stop_words
data(stop_words)

# add custom stop words for ASA chapters
addwords <- data.frame(c("2019","chapter","statistics","asa"), 
                       c("mkh","mkh","mkh","mkh"))
names(addwords) <- names(stop_words)
stop_words2 <- rbind(stop_words, addwords)

# setup custom functions for text mining
# of words (single word at a time)
# and bigrams (2-words together)
# these codes are based on examples
# in Julia Silge's Text Mining With R book

# make function for single words
# input data subset with
# only ID and district and textvar are used
wordscount <- function(df, textvar){
  tidywords <- tidytext::unnest_tokens(df, word, {{textvar}})
  countout <- tidywords %>% 
    filter(complete.cases(.)) %>%
    anti_join(stop_words2) %>%
    count(word, sort = TRUE)
  countout
}

# ct is needed if you want to look at
# higher or lower counts of the most common words used
# the default is set to > 2
wordsplot <- function(df, textvar, ct = 2){
  tidywords <- tidytext::unnest_tokens(df, word, {{textvar}})
  tidywords %>% 
    filter(complete.cases(.)) %>%
    anti_join(stop_words2) %>%
    count(word, sort = TRUE) %>%
    filter(n > ct) %>%
    mutate(word = reorder(word, n)) %>%
    ggplot(aes(word, n)) +
    geom_col() +
    xlab(NULL) +
    coord_flip()
}

wordscloud <- function(df, textvar){
  tidywords <- tidytext::unnest_tokens(df, word, {{textvar}})
  tidywords %>% 
    filter(complete.cases(.)) %>%
    anti_join(stop_words2) %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))
}

# add bigrams functions
bigramcount <- function(df, textvar){
  tidybigram <- 
    tidytext::unnest_tokens(df, bigram, {{textvar}}, 
                            token = "ngrams", n = 2)
  countout <- tidybigram %>%
    separate(bigram, c("word1", "word2"), sep = " ") %>%
    filter(!word1 %in% stop_words2$word) %>%
    filter(!word2 %in% stop_words2$word) %>%
    filter(complete.cases(.)) %>%
    count(word1, word2, sort = TRUE) %>%
    unite(bigram, word1, word2, sep = " ")
  countout
}
```

## "Other Chapter Activities" - Most Used Single Words (> 2x)

```{r}
# create df variable subset
df <- data2019 %>%
  select(REPORTID, DISTRICT, CHAPTERNAME, TXTOTHERACTIVITIES)

txtcount <- wordscount(df, "TXTOTHERACTIVITIES")

#knitr::kable(txtcount %>% filter(n>2),
#             caption = "Other Chapter Activities - Single Words Summary")

wordsplot(df, "TXTOTHERACTIVITIES", 2) 
```

## "Other Chapter Activities" - Single Words Wordcloud

```{r}
wordscloud(df, "TXTOTHERACTIVITIES")
```

## "Other Chapter Activities" - Bigrams (top 2-words)

```{r}
bicount <- bigramcount(df, "TXTOTHERACTIVITIES")

knitr::kable(bicount %>% filter(n>1),
             caption = "Other Chapter Activities - Bigram (2 word) Summary")
```

## Other Chapter Activity Details - Most Used Single Words (> 5x)

```{r}
# create df variable subset
df <- data2019 %>%
  select(REPORTID, DISTRICT, CHAPTERNAME, TXTOTHERDETAILS)

txtcount <- wordscount(df, "TXTOTHERDETAILS")

#knitr::kable(txtcount %>% filter(n>8),
#             caption = "Other Chapter ActivitY Details - Single Words Summary")

wordsplot(df, "TXTOTHERDETAILS", 5) +
  ggtitle("Other Chapter Activity Details - Most Used Single Words (mentioned more than 5x)")
```

## "Other Chapter Activity Details" - Single Words Wordcloud

```{r}
wordscloud(df, "TXTOTHERDETAILS")
```

## "Other Chapter Activity Details" - Bigrams (top 2-words)

```{r}
bicount <- bigramcount(df, "TXTOTHERDETAILS")

knitr::kable(bicount %>% filter(n>2),
             caption = "Other Chapter Activity Details - Bigram (2 word) Summary")
```

## "Use of Stimulus Funds" - Most Used Single Words (> 2x)

```{r}
# create df variable subset
df <- data2019 %>%
  select(REPORTID, DISTRICT, CHAPTERNAME, TXTSTIMULUSFUNDS)

txtcount <- wordscount(df, "TXTSTIMULUSFUNDS")

#knitr::kable(txtcount %>% filter(n>2),
#             caption = "Use of Stimulus Funds - Single Words Summary")

wordsplot(df, "TXTSTIMULUSFUNDS", 2) +
  ggtitle("Use of Stimulus Funds - Most Used Single Words (mentioned more than 2x)")
```

## "Use of Stimulus Funds" - Single Words Wordcloud

```{r}
wordscloud(df, "TXTSTIMULUSFUNDS")
```

## "Use of Stimulus Funds" - Bigrams (top 2-words)

```{r}
bicount <- bigramcount(df, "TXTSTIMULUSFUNDS")

knitr::kable(bicount %>% filter(n>1),
             caption = "Use of Stimulus Funds - Bigram (2 word) Summary")
```

## "How can ASA help your chapter?" - Most Used Single Words (> 2x)

```{r}
# create df variable subset
df <- data2019 %>%
  select(REPORTID, DISTRICT, CHAPTERNAME, TXTCHAPTERHELP)

txtcount <- wordscount(df, "TXTCHAPTERHELP")

#knitr::kable(txtcount %>% filter(n>2),
#             caption = "How can ASA help your chapter? - Single Words Summary")

wordsplot(df, "TXTCHAPTERHELP", 2) +
  ggtitle("How can ASA help your chapter? - Most Used Single Words (mentioned more than 2x)")
```

## "How can ASA help your chapter?" - Single Words Wordcloud

```{r}
wordscloud(df, "TXTCHAPTERHELP")
```

## "How can ASA help your chapter?" - Bigrams (top 2-words)

```{r}
bicount <- bigramcount(df, "TXTCHAPTERHELP")

knitr::kable(bicount %>% filter(n>1),
             caption = "How can ASA help your chapter? - Bigram (2 word) Summary")
```


